The Astropy Project

### 2017-10-29 main.tex
Update on Overleaf.

>>>>

\subsubsection{Accuracy of coordinate transformations}

In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have set up a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages \footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
